A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2019-06-01 paper/paper.Rnw
light editing

\mt{Model training is analogous to the human learning process. For example, a child learns to identify dogs by being presented with many labeled examples, such as when their parent uses the label ``dog" for an animal walking by. That child's understanding of dogs is then measured by how many dogs the child is able to correctly identify, and also by the number of cats it mistakenly calls ``dog". Similarly, CNN training is a series of stages, or ``epochs", where the model learns from the set of labeled training data, and that learning is measured through intermediate predictions of validation data.}

@@

\FloatBarrier

\subsection{Model Accuracy}\label{sec:model-accuracy}

\paragraph{Overall Accuracy} % Model-wise and class-by-class, w/ confusion matrix
\autoref{fig:roc-code} shows the ROC curve for the full model, and \autoref{fig:auc-code} shows the curve for each class. The full model has an AUC of 0.88, and the AUC for individual classes ranges from 0.81 (for line) to 0.91 (for bowtie and text). While the class performances do vary slightly, each ROC curve is the same general shape and performs significantly better than random chance.

@@

\FloatBarrier

As discussed in Section~\ref{sec:model-eval}, a confusion matrix is a cross-tabulation of the labels assigned to an image and the labels predicted by the model. In a single-label problem, an image belongs to only one category and the model predicts only one label, so applying the wrong label is equivalent to failing to apply the correct label. Thus, every possible combination of true label and applied prediction is represented in the two-dimensional/traditional confusion matrix. Extending the confusion matrix to more complex problems requires additional considerations.

@@

\autoref{fig:confusion_matrix} shows the general weaknesses of the model, but does not necessarily suggest where to look as to \emph{why} the model is not performing appropriately. In Sections~\ref{sec:model-consistency} and \ref{sec:heatmap}, alternative visualizations are used to better understand the weaknesses of the model when applied to actual images used to train, test, and validate the model.

>>>>

Model training is analogous to the human learning process. For example, a child learns to identify dogs by being presented with many labeled examples, such as when their parent uses the label ``dog" for an animal walking by. That child's understanding of dogs is then measured by how many dogs the child is able to correctly identify, and also by the number of other animals it mistakenly calls ``dog". Similarly, CNN training is a series of stages, or ``epochs", where the model learns from the set of labeled training data, and that learning is measured through intermediate predictions of validation data.

@@

\subsection{Model Accuracy}

\paragraph{Overall Accuracy} % Model-wise and class-by-class, w/ confusion matrix
\svp{You need to explain these terms. Your CC was written for statisticians, this paper is for practitioners. You need a MUCH gentler introduction to the idea of accuracy, errors, and ROC curves, as well as a lot more definitions for terms.}
\autoref{fig:roc-code} shows the ROC curve for the full model, and \autoref{fig:auc-code} shows the curve for each class. The full model has an AUC of 0.88, and the AUC for individual classes ranges from 0.81 (for line) to 0.91 (for bowtie and text). While the class performances do vary slightly, each ROC curve is the same general shape and performs significantly better than random chance.

@@

A confusion matrix is a cross-tabulation of the labels assigned to an image and the labels predicted by the model. In a single-label problem, an image belongs to only one category and the model predicts only one label, so applying the wrong label is equivalent to failing to apply the correct label. Thus, every possible combination of true label and applied prediction is represented in the two-dimensional/traditional confusion matrix. Extending the confusion matrix to more complex problems requires additional considerations.

@@

\autoref{fig:confusion_matrix} shows the general weaknesses of the model, but does not necessarily suggest where to look as to \emph{why} the model is not performing appropriately. %In Sections~\ref{sec:model-consistency} and \ref{sec:heatmap}, alternative visualizations are used to better understand the weaknesses of the model when applied to actual images used to train, test, and validate the model.
